---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# gamlss.lasso2

## Overview

**`gamlss.lasso2`** is an R package based on the original `gamlss.lasso` package available on [CRAN](https://cran.r-project.org/).
Compared to the original package, two major changes have been implemented in the function `gamlss.gnet`:
- Tuning via cross-validation (CV): The problem was that so far when doing tuning via CV, the lambda sequence would be different
  across all folds, thereby not allowing for a correct choice of lambda via CV (in fact, the output was incorrect this way).
  Now: the lambda sequence is chosen jointly for all folds and then handed to glmnet to compute the lasso path in each fold.
- 1-SE rule when tuning via CV: So far, `gamlss.gnet` would choose the lambda for which the cross-validated error plus `k.se`
  time the standard error was minimized. However, this does not correspond to the standard in the `glmnet` package, where
  the lambda is chosen to be the smallest value such that the cross-validated standard error is still within a `k.se`-standard
  error band around the minimum. This procedure was implemented also here.

## Installation

The source code is hosted on [github](https://github.com/jamon-R/gamlss.lasso2). To install the _R_ package, run the following code:

```{r, eval = FALSE, echo = TRUE}
devtools::install_github("jamon-R/gamlss.lasso2")
```

The package requires functionality from the packages `gamlss`, `glmnet`, `lars` and `Matrix`. All of those dependencies are available
on [CRAN](https://cran.r-project.org/).
